Supplementary Information

### 2021-02-11 doc/manuscript/MEE_manuscript.Rmd
list supplemental files

@@

>>>>

`r site_details_appendix_title`

@@

Figures `r all_recruitment_plots`. Density plots of core record start years by species for all sites.

Figures `r all_traditional_comparisons`. Comparison of our approach with traditional methods of identifying climate signals for four species.

Figures `r all_climwin`. Climwin output for water and temperature variable groups at all sites.

Figures `r all_GLS`. Best GLS models models excluding and including year for all sites.

`r SC_1970break_legend`

`r RW_interactions_all_legend `

`r BAI_interactions_all_legend`

Figures `r decadal_analysis_figs_all`. Relationships between $DBH$ and $BAI$ by decade for all sites.
